With all of the pieces for predictive auto-scaling in place, the final step is
making it so that a user running pods on the Kubernetes cluster can turn
prediction on and off. We seek a lightweight method for accomplishing this, so
as to not have to make drastic changes to the Kubernetes user interface before
being confident that predictive auto-scaling is a generally useful addition.

As was previously mentioned, Kubernetes makes it
possible to attach key/value pairs to any
resource through the concept of annotations. As was mentioned in the section on
recording pod initialization time, the annotations of an object are a useful way
to record information without going through the long process of making an
official update to the API for an object in Kubernetes. Thus, to turn on
auto-scaling for an individual auto-scaler object, we simply record in the annotations for
that object the key \textit{predictive} with the value \textit{true}. This
annotation can easily be done using Kubernetes command line
client \cite{k8s-kubectl-annotate}. For example,
if our auto-scaler had the name \textit{foo}, the following command would turn
on prediction.

\begin{minted}{bash}
  kubectl annotate hpa foo predictive=`true'
\end{minted}

It follows that auto-scaling could just as easily be turned off by rewriting the
annotated value to anything other than \textit{true}.

\begin{minted}{bash}
  kubectl annotate hpa foo predictive=`false'
\end{minted}

Within the code for determining the number of replica pods to create when
auto-scaling, we can easily check if the \textit{predictive} annotation is
\textit{true} for that particular auto-scaler. If the value is not set, or
is anything other than true, the auto-scaler will reactively auto-scale as normal.
This flexibility allows different auto-scalers to utilize different auto-scaling
methods. Additionally, it allows a single auto-scaler to utilize different
auto-scaling methods throughout its lifetime.

If the benefits of predictive auto-scaling are substantial, then it will make
sense to transition this value from one recorded in \textit{Annotations} to a
more permanent field defined a auto-scaler's
\textit{HorizontalPodAutoscalerSpec} object. A field entitled
\textit{Predictive} could be added to this object which, if set to true, would
turn on predictive auto-scaling. This addition would enable the user to
configure an
auto-scaler to perform predictively from the start, as opposed to having to first
create the auto-scaler and then turn on prediction. Making prediction a part of
the static configuration for an auto-scaler has the benefit of linking predictive
behavior with all other pod state, especially as configuration files are used
among multiple projects. However, until the benefits of predictive
auto-scaling are demonstrated, it does not make sense to undertake this effort.
